Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-13 article.qmd
Paraphrase typing errors

1. The variable name to which a component is assigned can be automatically saved in the component for introspection (i.e., `Oscilator.x.name == "x"`),
2. It provides a namespace such that allows easily definition of multiple independent models in the same script,
3. It allows IDEs to provide autocomplete and refactoring capabilities (`Oscillator.<TAB>` shows `x`, `v` and `eq`),
4. It allows creation of instances which can be composed into a bigger model (@fig-composition).

For the latter (???, not clear rephrase, probably after the next sentence),
it is important to add the type annotations,
as it can provide a signature autocompletion in IDEs supporting the `dataclass_transform` [@debontePEP681Data2021]:

Type annotations play a significant role in static type checking, helping to identify typing errors.
For instance, `Parameter`s can be assigned either a number or a time-dependent expression.
But can also be linked to an external variable when composing models.
As such, they (what?) cannot be used to parametrize the initial conditions of variables,
for which we have to use a `Constant` (@fig-ide). (message not clear, rephrase)

>>>>

1. The variable name to which a component is assigned can be automatically saved in the component for introspection (i.e., `Oscilator.x.name == "x"`),
2. It provides a namespace such that allows to easily define of multiple independent models in the same script,
3. It allows IDEs to provide autocomplete and refactoring capabilities (`Oscillator.<TAB>` shows `x`, `v` and `eq`),
4. It allows creation of instances which can be composed into a bigger model (@fig-composition).

For this last point,
IDEs that support `dataclass_transform` [@debontePEP681Data2021] can provide a tooltip with the expected signature (@fig-composition).
This requires the use of type annotations
which play a more significant role in static type checking,
as they can help to identify errors before running the code.
For instance, to parametrize the initial conditions of variables we have to use a `Constant`.
If we try to use a `Parameter`, which could be a time-dependent expression, it is flagged as a type error (@fig-ide).
